\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-07-18 paper/manuscript.tex
made multiple changes to the makefile

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Tue May 23 19:28:26 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lrrr}
		\hline
		Filetype & current & before & after \\ 
		\hline
		& 51455 & 13866 & 19199 \\ 
		pdf & 9646 & 5489 & 7544 \\ 
		jpg & 5216 & 1988 & 3512 \\ 
		html & 3767 & 17842 & 17596 \\ 
		aspx & 2832 & 4356 & 3271 \\ 
		png & 2714 & 2327 & 3684 \\ 
		gif & 1068 & 664 & 1077 \\ 
		JPG & 478 & 182 & 263 \\ 
		1 & 443 &  61 &  54 \\ 
		css & 390 & 265 & 518 \\ 
		js & 350 & 255 & 468 \\ 
		htm & 264 & 295 & 256 \\ 
		docx & 203 & 106 & 120 \\ 
		doc & 167 &  70 & 130 \\ 
		asp & 161 & 201 & 211 \\ 
		svg &  87 &  55 &  69 \\ 
		php &  83 & 157 & 241 \\ 
		\hline
	\end{tabular}
	\caption{The most common file types in scraped websites} 
\end{table}

\begin{landscape}
% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Tue May 23 19:35:22 2017
\begin{table}[ht]
	\centering
	\footnotesize
	\begin{tabular}{lrrrrrrrrr}
		\hline
		Website & current\_size & current\_files & before\_size & before\_files & after\_size & after\_files & size\_change & files\_change & control\_change \\ 
		\hline
		attica-in.gov & 61988 & 1417 & 7528 & 164 & 55956 & 1390 & 7.43 & 8.48 & 0.00 \\ 
		bedford.in.us & 57628 & 560 & 27452 & 182 & 46388 & 525 & 1.69 & 2.88 & 0.00 \\ 
		cityofboonvilleindiana.com & 9848 & 110 & 16996 & 172 & 20784 & 229 & 1.22 & 1.33 & 0.00 \\ 
		frankfort-in.gov & 205368 & 2652 & 12208 & 242 & 138360 & 1077 & 11.33 & 4.45 & 0.00 \\ 
		warsaw.in.gov & 298440 & 2117 & 26844 & 539 & 360400 & 2036 & 13.43 & 3.78 & 0.00 \\ 
		www.bloomington.in.gov & 131128 & 2713 & 443360 & 14384 & 247096 & 9640 & 0.56 & 0.67 & 0.00 \\ 
		www.brazil.in.gov & 43056 & 845 & 34472 & 625 & 55152 & 1214 & 1.60 & 1.94 & 0.00 \\ 
		www.carmel.in.gov & 2270016 & 8727 & 1919344 & 5361 & 899900 & 2219 & 0.47 & 0.41 & 0.00 \\ 
		www.ci.auburn.in.us & 183296 & 1025 & 21444 & 345 & 23564 & 211 & 1.10 & 0.61 & 0.00 \\ 
		www.cityoffortwayne.org & 2136424 & 4378 & 266784 & 3582 & 233600 & 3018 & 0.88 & 0.84 & 0.00 \\ 
		www.cityofhobart.org & 722000 & 2463 & 44192 & 650 & 62660 & 1037 & 1.42 & 1.60 & 0.00 \\ 
		www.evansvillegov.org & 6345932 & 11844 & 290784 & 1281 & 1697224 & 6853 & 5.84 & 5.35 & 0.00 \\ 
		www.gary.in.us & 373888 & 1227 & 121812 & 485 & 157140 & 719 & 1.29 & 1.48 & 0.00 \\ 
		www.huntingburg-in.gov & 388680 & 2496 & 8644 & 213 & 375900 & 1953 & 43.49 & 9.17 & 0.00 \\ 
		www.jasperindiana.gov & 561968 & 4013 & 55900 & 460 & 439072 & 2224 & 7.85 & 4.83 & 0.00 \\ 
		www.lakestation-in.gov &  48 &   2 & 7724 &  84 & 257272 & 1097 & 33.31 & 13.06 & 0.00 \\ 
		www.linton-in.gov &  32 &   1 &  24 &   2 &  24 &   2 & 1.00 & 1.00 & 0.00 \\ 
		www.madison-in.gov & 531044 & 1848 & 36636 & 575 & 191624 & 1444 & 5.23 & 2.51 & 0.00 \\ 
		www.martinsville.in.gov & 46792 & 1463 & 71628 & 1052 & 80944 & 800 & 1.13 & 0.76 & 0.00 \\ 
		www.monticelloin.gov & 33656 & 753 & 18120 & 448 & 100680 & 2104 & 5.56 & 4.70 & 0.00 \\ 
		www.newhavenin.org & 84364 & 626 & 2524 &  86 & 6792 & 334 & 2.69 & 3.88 & 0.00 \\ 
		www.richmondindiana.gov & 250968 & 1042 & 217252 & 918 & 401672 & 2422 & 1.85 & 2.64 & 0.00 \\ 
		www.southbendin.gov & 1264076 & 4749 & 454456 & 3286 & 1424136 & 2562 & 3.13 & 0.78 & 0.00 \\ 
		connersvillecommunity.com & 170688 & 569 & 162316 & 815 & 187276 & 808 & 1.15 & 0.99 & 1.00 \\ 
		www.batesvilleindiana.us & 166564 & 2348 & 39592 & 496 & 95696 & 1310 & 2.42 & 2.64 & 1.00 \\ 
		www.cityofrisingsun.com & 994956 & 3311 & 321400 & 1268 & 80848 & 868 & 0.25 & 0.68 & 1.00 \\ 
		www.cityofrockport-in.gov & 12068 &  98 & 5148 &  16 & 12068 &  98 & 2.34 & 6.12 & 1.00 \\ 
		www.elkhartindiana.org & 1132828 & 2345 & 5588 & 123 & 6204 & 223 & 1.11 & 1.81 & 1.00 \\ 
		www.elwoodcity-in.org & 224412 & 765 & 5000 & 123 & 139692 & 517 & 27.94 & 4.20 & 1.00 \\ 
		www.indy.gov & 5726048 & 9675 & 6119260 & 10451 & 4984080 & 7981 & 0.81 & 0.76 & 1.00 \\ 
		www.northvernon-in.gov & 272016 & 403 & 3132 & 112 & 289336 & 416 & 92.38 & 3.71 & 1.00 \\ 
		www.winchester-in.gov & 364592 & 2480 & 6508 & 135 & 45488 & 567 & 6.99 & 4.20 & 1.00 \\ 
		\hline
	\end{tabular}
	\caption{Number of files and size of websites} 
\end{table}
\end{landscape}

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Mar  1 11:55:24 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{rr}
		\hline
		& tf \\ 
		\hline
		tax & 176324 \\ 
		date & 98949 \\ 
		due & 97192 \\ 
		amt & 96382 \\ 
		town & 86726 \\ 
		value & 81119 \\ 
		total & 70825 \\ 
		parcel & 63589 \\ 
		county & 56201 \\ 
		market & 51758 \\ 
		east & 51357 \\ 
		full & 51199 \\ 
		nrth & 50566 \\ 
		book & 50306 \\ 
		deed & 50231 \\ 
		bill & 49719 \\ 
		acres & 48935 \\ 
		acct & 44871 \\ 
		csd & 43792 \\ 
		owners & 43510 \\ 
		res & 41803 \\ 
		family & 36883 \\ 
		fire & 35156 \\ 
		school & 33685 \\ 
		name & 30382 \\ 
		red & 30362 \\ 
		taxable & 30248 \\ 
		hook & 29902 \\ 
		homestead & 29287 \\ 
		outside & 28593 \\ 
		\hline
	\end{tabular}
	\caption{Top term frequencies for 10 test websites} 
\end{table}

@@

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 22 11:32:43 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lrrlrrl}
		\hline
		City & DemVotes & RepVotes & Winner & Change & Pop15 & url \\ 
		\hline
		Attica &  & 187 & Republican & 0 & 3117 & https://attica-in.gov/ \\ 
		Connersville & 1005 & 995 & Democratic & 1 & 13010 & http://connersvillecommunity.com/ \\ 
		Frankfort &  & 1748 & Republican & 0 & 16060 & http://frankfort-in.gov/ \\ 
		Huntingburg & 447 & 793 & Republican & 0 & 6035 & http://www.huntingburg-in.gov/ \\ 
		Indianapolis & 92830 & 56661 & Democratic & 1 & 862781 & http://www.indy.gov \\ 
		Lake Station & 1483 & 227 & Democratic & 0 & 12054 & http://www.lakestation-in.gov/ \\ 
		Linton & 785 & 692 & Democratic & 0 & 5284 & http://www.linton-in.gov/ \\ 
		Madison & 1192 & 1915 & Republican & 0 & 12040 & http://www.madison-in.gov/ \\ 
		Mitchell & 229 & 495 & Republican & 1 & 4252 & http://mitchell-in.com/ \\ 
		Monticello & 0 &  & Democratic & 0 & 5322 & http://www.monticelloin.gov/ \\ 
		North Vernon & 679 & 697 & Republican & 1 & 6619 & http://www.northvernon-in.gov/ \\ 
		Richmond & 3421 & 2731 & Democratic & 0 & 35854 & http://www.richmondindiana.gov/ \\ 
		Rockport & 286 & 272 & Democratic & 1 & 2223 & http://www.cityofrockport-in.gov/ \\ 
		South Bend & 8515 & 2074 & Democratic & 0 & 101516 & https://www.southbendin.gov/ \\ 
		Union City & 338 & 440 & Republican & 0 & 3447 & http://www.unioncity-in.gov/ \\ 
		Winchester & 606 & 524 & Democratic & 1 & 4769 & http://www.winchester-in.gov/ \\ 
		\hline
	\end{tabular}
	\caption{} 
\end{table}

>>>>

\input{tables/filetypes.tex}

\begin{landscape}
\input{tables/filenumbers.tex}
\end{landscape}

@@

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 22 11:32:43 2017
%\begin{table}[ht]
%	\centering
%	\begin{tabular}{lrrlrrl}
%		\hline
%		City & DemVotes & RepVotes & Winner & Change & Pop15 & url \\ 
%		\hline
%		Attica &  & 187 & Republican & 0 & 3117 & https://attica-in.gov/ \\ 
%		Connersville & 1005 & 995 & Democratic & 1 & 13010 & http://connersvillecommunity.com/ \\ 
%		Frankfort &  & 1748 & Republican & 0 & 16060 & http://frankfort-in.gov/ \\ 
%		Huntingburg & 447 & 793 & Republican & 0 & 6035 & http://www.huntingburg-in.gov/ \\ 
%		Indianapolis & 92830 & 56661 & Democratic & 1 & 862781 & http://www.indy.gov \\ 
%		Lake Station & 1483 & 227 & Democratic & 0 & 12054 & http://www.lakestation-in.gov/ \\ 
%		Linton & 785 & 692 & Democratic & 0 & 5284 & http://www.linton-in.gov/ \\ 
%		Madison & 1192 & 1915 & Republican & 0 & 12040 & http://www.madison-in.gov/ \\ 
%		Mitchell & 229 & 495 & Republican & 1 & 4252 & http://mitchell-in.com/ \\ 
%		Monticello & 0 &  & Democratic & 0 & 5322 & http://www.monticelloin.gov/ \\ 
%		North Vernon & 679 & 697 & Republican & 1 & 6619 & http://www.northvernon-in.gov/ \\ 
%		Richmond & 3421 & 2731 & Democratic & 0 & 35854 & http://www.richmondindiana.gov/ \\ 
%		Rockport & 286 & 272 & Democratic & 1 & 2223 & http://www.cityofrockport-in.gov/ \\ 
%		South Bend & 8515 & 2074 & Democratic & 0 & 101516 & https://www.southbendin.gov/ \\ 
%		Union City & 338 & 440 & Republican & 0 & 3447 & http://www.unioncity-in.gov/ \\ 
%		Winchester & 606 & 524 & Democratic & 1 & 4769 & http://www.winchester-in.gov/ \\ 
%		\hline
%	\end{tabular}
%	\caption{} 
%\end{table}
